Notes on the Godunov Step in {\tt MAESTRO} and {\tt VARDEN}

### 2008-04-17 docs/Godunov_notes/paper.tex
listing some differences between MAESTRO and VARDEN

These are working notes for the Godunov step in {\tt MAESTRO}.
\section{Differences Between These Notes and the Code}
\begin{enumerate}
\item In both equations (\ref{Radial utrans_L}) and (\ref{Radial utrans_R}), we are omitting the terms in equation (\ref{Perturbational Velocity Equation}) proportional to $w_0$ (by using $\wt$ rather than $w$ as the advection speed) and $(\Ubt\cdot\eb_r)$ (by omitting the term altogether).
\item In equation (\ref{Force Term}), we do not include the term proportional to $\partial\pi_0/\partial r$.
\end{enumerate}
\section{Questions}
\begin{enumerate}
\item We need to re-examine when to include the term proportional to $(\Ubt\cdot\eb_r)$ in equation (\ref{Perturbational Velocity Equation}) when we do a 1D extrapolation of the radial velocity.  For example, equations (\ref{Radial utrans_L}) and (\ref{Radial utrans_R}) include it, but equations (\ref{1D wt_L extrap}) and (\ref{1D wt_R extrap}) do not.
\item In equations (\ref{wt_L Extrapolation}) and (\ref{wt_R Extrapolation}), we could also compute the term proportional to $\partial w_0/\partial r$ by averaging $w^{\trans}$.
\end{enumerate}
\cleardoublepage
\section{Computing $\Ubt^{\trans}$ in {\tt MAESTRO}}
In {\tt advance\_premac}, we call the function {\tt mkutrans}, which computes the edge-centered transverse velocities, $\Ubt^{\trans}$.  These transverse velocities do not contain $w_0$, so immediately following the call to {\tt mkutrans}, we call {\tt addw0} to compute $\Ub^{\trans}$ from $\Ubt^{\trans}$.  We will only compute the normal component of velocity at each face.\\

>>>>

These are working notes for the Godunov step in {\tt MAESTRO} and {\tt VARDEN}.
\section{Differences Between These Notes and the Code}
\begin{enumerate}
\item In both equations (\ref{Radial utrans_L}) and (\ref{Radial utrans_R}), we are omitting the terms in equation (\ref{Perturbational Velocity Equation}) proportional to $w_0$ (by using $\wt$ rather than $w$ as the advection speed) and $(\Ubt\cdot\eb_r)$ (by omitting the term altogether).
\item In equation (\ref{Force Term}), we do not include the term proportional to $\partial\pi_0/\partial r$.
\end{enumerate}
\section{Questions}
\begin{enumerate}
\item We need to re-examine when to include the term proportional to $(\Ubt\cdot\eb_r)$ in equation (\ref{Perturbational Velocity Equation}) when we do a 1D extrapolation of the radial velocity.  For example, equations (\ref{Radial utrans_L}) and (\ref{Radial utrans_R}) include it, but equations (\ref{1D wt_L extrap}) and (\ref{1D wt_R extrap}) do not.
\item In equations (\ref{wt_L Extrapolation}) and (\ref{wt_R Extrapolation}), we could also compute the term proportional to $\partial w_0/\partial r$ by averaging $w^{\trans}$.
\end{enumerate}
\section{Differences Between {\tt MAESTRO} and {\tt VARDEN}}
\begin{enumerate}
\item {\tt VARDEN} does not use the concept of $w_0$, so there is no such thing as $\Ubt$ either.  {\tt VARDEN} only does Cartesian problems.
\item {\tt VARDEN} does not use the concept of $\Ub^{\trans}$, but rather in {\tt advance\_premac}, the function {\tt velpred} computes $\Ub^{\mac,*}$ directly.
\item {\tt VARDEN} uses characteristic tracing in the Taylor series extrapolation for $\Ub^{\mac,*}$.
\item {\tt VARDEN} uses an ``FPU'' type algorithm to get both $\Ub^{\edge}$ and $s^{\edge}$, whereas {\tt MAESTRO} uses the ``FPU'' algorithm for $s^{\edge}$, but not $\Ub^{\edge}$
\end{enumerate}
\cleardoublepage
\section{Computing $\Ubt^{\trans}$ in {\tt MAESTRO}}
In {\tt advance\_premac}, we call the function {\tt mkutrans}, which computes the edge-centered transverse velocities, $\Ubt^{\trans}$.  These transverse velocities do not contain $w_0$, so immediately following the call to {\tt mkutrans}, we call {\tt addw0} to compute $\Ub^{\trans}$ from $\Ubt^{\trans}$.  We will only compute the normal component of velocity at each face.\\
